%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE 
%----------------------------------------------------------------------------------------

\textsc{Verizon Business} \hfill Colorado Springs, CO\\
Senior Engineer - Network and Information Security \hfill \textsc{March 2005} - \textsc{May 2012}

\textbf{Network Computing Security}\\
Acted as a top engineer for Verizon’s wireline security organization.
Responsible for various security projects and activities including:

\begin{itemize}
\item
Responsible for security review of network and application architecture for
Verizon Digital Media Services.  This included approving network architecture
documents and application architecture documents.  Required to participate in a
leadership position in cross functional technical teams to build digital media
services for a projected \$500B industry.

\item
Technical team lead for design and development of a distributed VPN system.
Responsible for designing VPN using Juniper Unified Access Control.  Also
responsible for designing and implementing enterprise self-service system to
facilitate delegated management of VPN access rules.

\item
Lead team responsible for reviewing and approving firewall change requests.
Responsibilities included handling request escalations and assisting in dispute
resolution regarding policy interpretation.

\item
Assisted with writing and reviewing company security policy

\item
Responsible for design and development of MAC and IP address correlation tool
for real-time IP ownership resolution.  This tool was used by most of Verizon
Business’ security and operations personnel during routine network tasks as well
as rapid security incident response

\item
Tool development for security assessment and auditing. These tools were mostly
Perl scripts for parsing various network configs and reporting on security
issues.  Some tools were developed on-demand during rapid incident response

\item 
Development of Access Control List database for tracking changes to several
thousand router based ACLs. System was written in Java utilizing Spring MVC,
Hibernate, MySQL and a custom written RCS back-end

\end{itemize}

