%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE 
%----------------------------------------------------------------------------------------

\textsc{Verizon} \hfill \textsc{March 2005-July 2013}

\textbf{Global Network Planning} \hfill Colorado Springs, CO\\
Principal Member of Technical Staff \hfill \textsc{May 2012} - \textsc{July 2013}

Responsible for developing network architecture plans and long term
vision for Verizon’s global internet backbone.

\begin{itemize}
\item
Responsible for all network infrastructure for the Verizon digital media
integration lab including automating network changes in the lab.  Primarily
dealt with Juniper SRX series firewalls, Juniper MX series routers and
Arista modular switches.

\item
Developed network architecture plans for several Verizon Digital Media Services
(VDMS) projects.  Architecture plans included vlan layouts, MPLS VPN overlay
design, BGP policy design and multicast content delivery architecture.

\item
Worked with other members of the team to research Software Designed Networking
(SDN) and Network Function Virtualization (NFV) for long term global network
plan.  Lab tested technology including OpenFlow and VXLAN.  Worked with team
to develop initial concept of a virtualized BGP route reflector.
\end{itemize}

\textbf{Network Computing Security} \hfill Colorado Springs, CO\\
Principal Member of Technical Staff \hfill \textsc{November 2010} - \textsc{May 2012}

\begin{itemize}
\item
Responsible for security review of network and application architecture for
Verizon Digital Media Services.  This included approving network architecture
documents and application architecture documents.  Required to participate in a
leadership position in cross functional technical teams to build digital media
services for a projected \$500B industry.

\item
Responsible for reviewing and approving all firewall changes for Verizon Digital
Media Services.  This included reviewing firewall change requests to determine
policy compliance.

\item
Technical team lead for design and development of a distributed VPN system.
Responsible for designing VPN using Juniper Unified Access Control.  Also
responsible for designing and implementing enterprise self-service system to
facilitate delegated management of VPN access rules.
\end{itemize}


\textbf{Network Computing Security} \hfill Colorado Springs, CO\\
Senior Engineer - Network and Information Security \hfill \textsc{August 2006} - \textsc{November 2010}

\begin{itemize}
\item
Responsible for reviewing and approving enterprise firewall change requests.
Responsibilities included handling request escalations and assisting in dispute
resolution regarding policy interpretation.

\item
Responsible for team managing enterprise VPN plant.  Managed 20 Nortel Contivity VPN servers
averaging 40,000 - 50,000 concurrent sessions daily.
\end{itemize}


\textbf{Network Computing Security} \hfill Colorado Springs, CO\\
Network Engineer - Network and Information Security \hfill \textsc{March 2005-August 2006}

\begin{itemize}
\item
Responsible for design and development of MAC and IP address correlation tool
for real-time IP ownership resolution.  This tool was used by most of Verizon
Business’ security and operations personnel during routine network tasks as well
as rapid security incident response

\item
Tool development for security assessment and auditing. These tools were mostly
Perl scripts for parsing various network configs and reporting on security
issues.  Some tools were developed on-demand during rapid incident response

\item 
Development of Access Control List database for tracking changes to several
thousand router based ACLs. System was written in Java utilizing Spring MVC,
Hibernate, MySQL and a custom written RCS back-end
\end{itemize}

